### 2019-08-20 Docs/mg/mg.tex

\section{\amrex\ Multigrid Philosophy}

Here we describe some of the general ideas behind the \amrex\
multigrid (MG).

We solve MG on an AMR hierarchy, which means in places we will encounter
C-F interfaces.  The \amrex\ MG will modify the stencil for the Laplacian
at C-F interfaces to ensure the correct solution to the Poisson equation
across these interfaces.  There is no correction step needed in this
case (this differs from \cite{ricker:2008}).

The MG solver always works with jumps of $2\times$ between levels.  In 
some codes (but not \maestro) we can have jumps of $4\times$ between
levels.  \amrex\ uses a {\tt mini\_cycle} in these cases, effectively
inserting a multigrid level between the two AMR levels and doing a mini
V-cycle.

The MG solvers are located in {\tt amrex/Src/LinearSolvers/F\_MG/}.
There are two MG solvers, for cell-centered and nodal data.
Generally, the routines specific to the cell-centered solver will have
{\tt cc} in their name, and those specific to the nodal solver will have
{\tt nd} in their name.

@@

The \mgtower\ is a special Fortran derived type that carries all the
information required for a \amrex\ multigrid solve.

@@

\item {\tt ss}: The stencil itself---for each zone, this gives the 
  coefficients of the terms in the Laplacian, with the convection that
  the `0' term is located in the current cell and the other terms are
  the $\pm 1$ off the current cell in each direction.

@@

There are several bottom solvers available in \amrex.  For \maestro.
These are set through the {\tt mg\_bottom\_solver} (MAC/cell-centered)
and {\tt hg\_bottom\_solver} (nodal) runtime parameters.
The allowed values are:
\begin{itemize}

@@

\maestro\ uses multigrid to enforce the velocity constraint through
projections at the half-time (the MAC projection) and end of the time
step (the HG projection).  Two multigrid solvers are provided by
\amrex---one for cell-centered data and one for node-centered (nodal)
data.  Both of these are used in \maestro.

>>>>

\section{\fboxlib\ Multigrid Philosophy}

Here we describe some of the general ideas behind the \fboxlib\
multigrid (MG).

We solve MG on an AMR hierarchy, which means in places we will encounter
C-F interfaces.  The \fboxlib\ MG will modify the stencil for the Laplacian
at C-F interfaces to ensure the correct solution to the Poisson equation
across these interfaces.  There is no correction step needed in this
case (this differs from \cite{ricker:2008}).

The MG solver always works with jumps of $2\times$ between levels.  In 
some codes (but not \maestro) we can have jumps of $4\times$ between
levels.  \fboxlib\ uses a {\tt mini\_cycle} in these cases, effectively
inserting a multigrid level between the two AMR levels and doing a mini
V-cycle.

The MG solvers are located in {\tt FBoxLib/Src/LinearSolvers/F\_MG/}.
There are two MG solvers, for cell-centered and nodal data.
Generally, the routines specific to the cell-centered solver will have
{\tt cc} in their name, and those specific to the nodal solver will have
{\tt nd} in their name.

@@

The \mgtower\ is a special Fortran derived type that carries all the
information required for a \fboxlib\ multigrid solve.

@@

\item {\tt ss}: The stencil itself---for each zone, this gives the 
  coefficients of the terms in the Laplacian, with the convention that
  the `0' term is located in the current cell and the other terms are
  the $\pm 1$ off the current cell in each direction.

@@

There are several bottom solvers available in \fboxlib.  For \maestro.
These are set through the {\tt mg\_bottom\_solver} (MAC/cell-centered)
and {\tt hg\_bottom\_solver} (nodal) runtime parameters.
The allowed values are:
\begin{itemize}

@@

\maestro\ uses multigrid to enforce the velocity constraint through
projections at the half-time (the MAC projection) and end of the time
step (the HG projection).  Two multigrid solvers are provided by
\fboxlib---one for cell-centered data and one for node-centered (nodal)
data.  Both of these are used in \maestro.
